Random Forests

### 2023-11-08 src/la_RF.Rmd
rf

df <- df %>% filter(!is.na(ladcd)) %>% 
  complete(ladcd, year) %>% 
  replace(is.na(.), 0)

@@

```{r, eval=F}
firms <- read_csv("https://www.nomisweb.co.uk/api/v01/dataset/NM_142_1.data.csv?geography=1811939329...1811939332,1811939334...1811939336,1811939338...1811939428,1811939436...1811939442,1811939768,1811939769,1811939443...1811939497,1811939499...1811939501,1811939503,1811939505...1811939507,1811939509...1811939517,1811939519,1811939520,1811939524...1811939570,1811939575...1811939599,1811939601...1811939628,1811939630...1811939634,1811939636...1811939647,1811939649,1811939655...1811939664,1811939667...1811939680,1811939682,1811939683,1811939685,1811939687...1811939704,1811939707,1811939708,1811939710,1811939712...1811939717,1811939719,1811939720,1811939722...1811939730,1811939757...1811939767&date=latestMINUS10&industry=37748736&employment_sizeband=0&legal_status=0&measures=20100") %>% 
  dplyr::select(GEOGRAPHY_CODE, OBS_VALUE) %>% #GEOGRAPHY_NAME, 
  rename(ladcd = GEOGRAPHY_CODE,
         firms = OBS_VALUE)

@@

path.lookup <- paste0(path, "/data/raw/Local_Authority_District_to_Region_(April_2021)_Lookup_in_England.csv")  
lookup.region <- read_csv(path.lookup)%>% dplyr::select(LAD21CD, RGN21CD)

df <- df %>% left_join(lookup.region, by = c("ladcd" = "LAD21CD")) %>% 
  relocate(RGN21CD, .after=year)
```

@@

- [x] read more about trainColntrol
- [ ] other variables, check regressions, N/S?
- [x] reproducible
- [ ] n vs. log(n/n.lag), %>% mutate(n.lag = n.lag + 0.00001, n = n + 0.00001, way to bring S?
- [ ] ceter or scale with preProcess??
- [ ] direction of relationship, or cor()
- [ ]importance over time
- [ ] spatial sampling
- [ ] OA

@@

#(8 is the number of tuning parameter, mtry for rf, here equal to ncol(iris)-2)
for(i in 1:10) seeds[[i]]<- sample.int(n=1000, 8)

@@

for (t in years){
  tplus1 <- t + 1
  set.seed(71)
  model.all <- train(n ~ area + dist + dist.retail + London + 
                     n.lag + n.slag + n.l.slag + n.nearest.city + year,
                     data = df %>% filter(year==t | year==tplus1),
                     trControl = tc,
                     method = "rf", 
                     importance = TRUE)
  assign(paste0("model.all",as.character(t + 1)), model.all)
}

@@

@@

@@

@@

# drop 2000 and select variables form total
df.no1997_1 <- df %>% 
  filter(year!=1996 & year!=1997 & year!=1998) %>% 
  dplyr::select(ladcd, year, n)

@@

# calculate metrics for every year
rf.year.all.metrics <- lapply(pred.by.year.all.list, function(x) postResample(pred = x$predictions,
                                                                     obs = x$n))
rf.year.all.metrics %>% as.data.frame() %>%
  round(2) %>%
  kable()

>>>>

## REPLACE WITH 0.1 INSTEAD OF OF 0 FOR THE GROWTH
df <- df %>% filter(!is.na(ladcd)) %>% 
  complete(ladcd, year) %>% 
  replace(is.na(.), 0)

@@

```{r, eval=T}
firms <- read_csv("https://www.nomisweb.co.uk/api/v01/dataset/NM_142_1.data.csv?geography=1811939329...1811939332,1811939334...1811939336,1811939338...1811939428,1811939436...1811939442,1811939768,1811939769,1811939443...1811939497,1811939499...1811939501,1811939503,1811939505...1811939507,1811939509...1811939517,1811939519,1811939520,1811939524...1811939570,1811939575...1811939599,1811939601...1811939628,1811939630...1811939634,1811939636...1811939647,1811939649,1811939655...1811939664,1811939667...1811939680,1811939682,1811939683,1811939685,1811939687...1811939704,1811939707,1811939708,1811939710,1811939712...1811939717,1811939719,1811939720,1811939722...1811939730,1811939757...1811939767&date=latestMINUS10&industry=37748736&employment_sizeband=0&legal_status=0&measures=20100") %>% 
  dplyr::select(GEOGRAPHY_CODE, OBS_VALUE) %>% #GEOGRAPHY_NAME, 
  rename(ladcd = GEOGRAPHY_CODE,
         firms = OBS_VALUE)

@@

path.lookup <- paste0(path, "/data/raw/Local_Authority_District_to_Region_(April_2021)_Lookup_in_England.csv")  
lookup.region <- read_csv(path.lookup) %>% dplyr::select(LAD21CD, RGN21CD)

df <- df %>% left_join(lookup.region, by = c("ladcd" = "LAD21CD")) %>% 
  relocate(RGN21CD, .after=year)

# North/South
#lookup.region %>% distinct(RGN21NM, .keep_all = T)
south <- c("E12000007", "E12000008", "E12000009" )
df <- df %>% mutate(south = ifelse(RGN21CD %in% south, 1, 0))

# For growth:
#df <- df %>% mutate(growth = log(n/n.lag))

@@

- [x] read more about trainColntrol
- [ ] other variables, LA Classification, check regressions, 
- [x] N/S
- [x] reproducible
- [ ] n vs. log(n/n.lag), %>% mutate(n.lag = n.lag + 0.00001, n = n + 0.00001, way to bring S?
- [1] center or scale with preProcess??
- [ ] direction of relationship, or cor()
- [x] importance over time
- [2] spatial sampling
- [ ] OA

@@

#(8 is the number of tuning parameter, mtry for rf, here equal to ncol(iris)-2)
for(i in 1:10) seeds[[i]]<- sample.int(n=1000, 9) # 9 after adding South

@@

for (t in years){
  tplus1 <- t + 1
  set.seed(71)
  model.all <- train(n ~ area + dist + dist.retail + London + south + #growth ~ 
                      n.slag + n.l.slag + n.nearest.city + year, #n.lag +
                     data = df %>% filter(year==t | year==tplus1), #%>% 
                       # mutate(growth = ifelse(growth == -Inf | growth == Inf, NA, growth)) %>% 
                       # mutate(growth = ifelse(is.na(growth), 0, growth)), 
                     #%>% mutate(growth = ifelse(growth== -Inf | growth == Inf, NA, growth))
                     trControl = tc,
                     method = "rf", #"rpart", # rf lm
                     na.action = na.omit,
                     importance = TRUE)
  assign(paste0("model.all",as.character(t + 1)), model.all)
}

@@

# df %>% filter(growth == Inf) 
# log(n/n.lag)

@@

```{r}
help <- lapply(fit.model.all, function(x) varImp(x)) 
help <- lapply(help, function(x) x[[1]])
help <- do.call("rbind", help)

importance <- help %>% rownames_to_column() %>% 
  mutate(feature = gsub("model.all[0-9]+.", "", rowname),
         year = gsub(".*?([0-9]+).*", "\\1", rowname)) %>% 
  rename(importance = Overall) %>% 
  relocate(importance, .after = year) %>% 
  dplyr::select(-rowname)

importance %>% ggplot() +
  geom_line(aes(x=year, y = importance, color = feature, group = feature), size = 1) +
  scale_color_discrete(name = "Features") +
  #scale_linetype_manual(name = "Website density regressions111") 
  ylab("Importance") + 
  ggtitle("Feature importance") +
  theme_minimal() +
  theme(axis.title.x=element_blank(),
        plot.title = element_text(hjust = 0.5))

```

@@

# growth or n

@@

# drop 2000 and select variables form total
df.no1997_1 <- df %>% 
  filter(year!=1996 & year!=1997 & year!=1998) %>% 
  dplyr::select(ladcd, year, n) # CHANGE n WITH growth

@@

# calculate metrics for every year
rf.year.all.metrics <- lapply(pred.by.year.all.list, function(x) postResample(pred = x$predictions,
                                                                     obs = x$n))  # CHANGE n WITH growth
rf.year.all.metrics %>% as.data.frame() %>%
  round(2) %>%
  kable()
